Forschungsprojekt

### 2020-10-19 documentation/presentation/main.tex
dinge
Kleine Änderungen an Präsentation

\section{Overview}
\vfill
\begin{enumerate}
	\item Preliminaries
	\begin{itemize}
	\item Basics
	\item Computation Styles
	\item Hugepages
	\end{itemize}
	\item Frameworks
	\item Evaluation
	\begin{itemize}
	\item Research vs. Production Case
	\item Results
	\item Impact of Hugepages on Galois
	\end{itemize}
	\item Conclusion
\end{enumerate}
\vfill

% In the past years several graph processing systems emerged.
% Graphs are growing fast and are becoming increasingly popular. Many problems can be modeled and solved using graphs.

@@

% \section{Frameworks}

@@

% \begin{multicols}{2}
% \begin{description}
% 	\item[$\color{Galois}\blacksquare$ Galois] is a general purpose library designed for parallel programming
% 	\begin{itemize}
% 		\item Version 6.0 from 29\textsuperscript{th} June 2020 used 
% 	\end{itemize}
% 	\item[$\color{Gemini}\blacksquare$ Gemini] uses a distributed message-based approach from scratch
% 	\begin{itemize}
% 		\item Version from 2\textsuperscript{nd} November 2016 used
% 		\item Version contains bugs that had to be fixed 
% 	\end{itemize}

% 	\columnbreak

% 	\item[$\color{Giraph}\blacksquare$ Giraph] is built on Apache Hadoop, a large scale data processing infrastructure
% 	\begin{itemize}
% 		\item Version 1.3 from 8\textsuperscript{th} May 2020 used
% 		\item BFS is not natively supported 
% 		\item state-of-the-art, but not NUMA-aware
% 	\end{itemize}
% 	\item[$\color{Ligra}\blacksquare$ Ligra] dynamically switches between push and pull style
% 	\begin{itemize}
% 		\item Version from 14\textsuperscript{th} August 2019
% 	\end{itemize}
% 	\item[$\color{Polymer}\blacksquare$ Polymer] optimizes data layout and memory access strategies
% 	\begin{itemize}
% 		\item Version from 28\textsuperscript{th} August 2018
% 	\end{itemize}
% \end{description}
% \end{multicols}

% Features, version, numa, message passing/sharememory, bfs fehlt?

\newgeometry{paperwidth=28.1cm, paperheight=18cm, left=2cm, right=2cm, top=0.7cm,bottom=1cm,includefoot,heightrounded}
\section{Frameworks}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcccp{8cm}p{6cm}}
	Framework&Version&NUMA&Dist.&\multicolumn{1}{c}{Features}&\multicolumn{1}{c}{Notes}\\
	\toprule
	$\color{Galois}\blacksquare$\ \bf Galois&29.06.2020&\checkmark&(\checkmark)&general purpose library designed for parallel programming&Distributed using Gluon\\\midrule
	$\color{Gemini}\blacksquare$\ \bf Gemini&02.11.2016&\checkmark&\checkmark&distributed message-based approach from scratch&Version contains bugs that had to be fixed \\\midrule
	$\color{Giraph}\blacksquare$\ \bf Giraph&08.05.2020&X&\checkmark&built on Apache Hadoop&BFS is not natively supported \\\midrule
	$\color{Ligra}\blacksquare$\ \bf Ligra&14.08.2019&\checkmark&X&dynamically switches between push and pull style&\\\midrule
	$\color{Polymer}\blacksquare$\ \bf Polymer&28.08.2018&\checkmark&X&optimizes data layout and memory access strategies&\\
\end{tabular}

>>>>

\section{Overview}
{\large
\begin{enumerate}
	\item Preliminaries
	\begin{itemize}
	\item Basics
	\item Computation Styles
	\item Hugepages
	\end{itemize}
	\item Frameworks
	\item Evaluation
	\begin{itemize}
	\item Research vs. Production Case
	\item Results
	\end{itemize}
	\item Conclusion and Outlook
\end{enumerate}
}
% In the past years several graph processing systems emerged.
% Graphs are growing fast and are becoming increasingly popular. Many problems can be modeled and solved using graphs.

@@

@@

\newgeometry{paperwidth=28.1cm, paperheight=18cm, left=2cm, right=2cm, top=0.7cm,bottom=1cm,includefoot,heightrounded}
\section{Frameworks}
\vfill
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcccp{8cm}p{6cm}}
	Framework&Version&NUMA&Dist.&\multicolumn{1}{c}{Features}&\multicolumn{1}{c}{Notes}\\
	\toprule
	$\color{Galois}\blacksquare$\ \bf Galois&29.06.2020&\checkmark&(\checkmark)&general purpose library designed for parallel programming, Hugepage support&distributed using Gluon\\\midrule
	$\color{Gemini}\blacksquare$\ \bf Gemini&02.11.2016&\checkmark&\checkmark&distributed message-based approach from scratch&version contains bugs that had to be fixed \\\midrule
	$\color{Giraph}\blacksquare$\ \bf Giraph&08.05.2020&X&\checkmark&built on Apache Hadoop&BFS is not natively supported \\\midrule
	$\color{Ligra}\blacksquare$\ \bf Ligra&14.08.2019&\checkmark&X&dynamically switches between push and pull style&\\\midrule
	$\color{Polymer}\blacksquare$\ \bf Polymer&28.08.2018&\checkmark&X&optimizes data layout and memory access strategies&\\
\end{tabular}
\vfill
